---
title: "Another R Style Guide"
author: "Charles B. Walters"
output: html_notebook
---

***
"Good coding style is like using correct punctuation. You can manage without it, 
but it sure makes things easier to read."
- Hadley Wickham

As I sharpen my skills in R, this will serve as a living document, a reflection
of the R style parameters I will endeavor to adhere to for clarity, consistency,
and fluidity. It has been loosely modeled from Hadley Wickham's *Advanced R*

*Last update: 3/11/2021*

***

## General
### File Names
File names should be clear, purposeful, concise, and end in .R.

Yay
```{r}
fit-models.R
utility-functions.R
```
Nay
```{r}
allofthethingsforprojectxyz.r
JulyFinalStats.r
```

### Object Names
Variable and function names are all lowercase, and words are to be separated 
with an underscore (_). Objects containing primary data structures may use capital letters 
to remain distinct from other objects. Like file names, object names should be 
clear, purposeful, and concise.

Yay
```{r}
day_one_observations
day_1_results
```
Nay
```{r}
DayOneObs
test1
```

### Commenting
Commenting in R scripts is useful for explaining syntax where needed. Comments should be used
for "why" rather than "what." Clarity, brevity, and purpose are paramount. 

Yay
```{r}
# Setting factors for use with conditional proportions
```
Nay
```{r}
# This is me renaming variable levels
```

***

## Syntax
### Spacing
Operators have single spaces on each side with the exception of "/" and ":". Commas have single spaces after, never before.

Yay
```{r}
day_one_mean <- c((2 + 3 + 4 + 6)/4)
```
Nay
```{r}
day_one_mean<-c((2+3+4+6)/4)
```

### Indentation
Code is indented with two spaces. If a function runs more than one line, 
however, indent subsequent lines to the start of the function's arguments.

Yay
```{r}
long_function_name <- barplot(a = "a long argument", 
                              b = "another argument",
                              c = "another long argument")
```
Nay
```{r}
long_function_name <- barplot(a = "a long argument", b = "another argument", 
c = "another long argument")
```

### Assignment
<- and -> are the appropriate assignment operators.

Yay
```{r}
x <- c(1:10)
```
Nay
```{r}
x = c(1:10)
```

***